Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
Add files via upload

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races). The data is collected via surveys and supplied by state agencies to NCES [@USDeptCommerce].

@@

We extended Jack and Oster's research by also looking at the shares of White and Asian students. We found that districts with "High" and "Low" shares of White students had an average of 55 and 23 days in virtual schooling, respectively. Likewise, we found that districts with "High" and "Low" shares of Asian students had average of 40 and 38 days in virtual schooling, respectively. These results point to the following: White students appear to be further enfranchised by having greater access to in-person learning, in contrast to historically and currently disadvantaged Black and Hispanic students. No such conclusions can be drawn for Asian students, for whom the variation in the number of virtual days between "High" and "Low" districts is too small to be considered.

>>>>

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races). Thanks to partnerships with state education authorities and organisations, NCES is authorised to collected data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024]. Its National Forum on Education Statistics then collects, processes and reports elementary and local education statistics [@Encyclopedia_2024].

@@

We extended Jack and Oster [-@Jack_Oster_2023]'s research by also looking at the shares of White and Asian students. We found that districts with "High" and "Low" shares of White students had an average of 55 and 23 days in virtual schooling, respectively. Likewise, we found that districts with "High" and "Low" shares of Asian students had average of 40 and 38 days in virtual schooling, respectively. These results point to the following: White students appear to be further enfranchised by having greater access to in-person learning, in contrast to historically and currently disadvantaged Black and Hispanic students. No such conclusions can be drawn for Asian students, for whom the variation in the number of virtual days between "High" and "Low" districts is too small to be considered.
